\pagestyle{plain}
\begin{center}


\section*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements} 


\end{center}
This project could not have been accomplished without the help and support of so many incredible people.

I would like to start off by thanking Professor Phan. I took `ENGS26: Control Theory' with him in the Spring of my Sophomore year and by the end of the term had changed my major concentration. He presented topics in clear, understandable, and intuitive ways which I tried to replicate in this thesis. It was in his class `ENGS145: Modern Control Theory' where the base ideas for this Thesis were formed, and `ENGS149: System Identification' where I finally mustered the courage to ask him to be my advisor. I do not think a better mentor for a project such as this exists. I challenge you to find any other Professor who would be willing to stay around for hours on a Friday afternoon-turned-night to help work through proofs on the board, identify sources of errors, and provide paths forward for every problem that arose. It is my hope that the presented work is worthy of his time and dedication to my studies.

Next must come my partner Audrey Herrald. She has sat through hours of me frowning at a notebook, scratching at a chalkboard, banging at my keyboard, and generally thinking aloud - without complaint; all while going through Med School herself. She has heard all the material to follow more times than anyone, and has been a key figure of support to ensure I maintain priorities, focus, and sanity throughout this process.

The come my parents, Drs. Katherine and Keith Dunleavy. I have been truly fortunate in life to have the most amazing, loving, and supportive parents. All through my life, no matter what I did or how I did it, they have been there for me. Cheering me on from Little League to Robotics Competitions to Track Meets. No matter how much work I have ever had (or little I claimed to have), they provided me with every tool I needed to succeed. They have taught me through example what it means to work hard, take pride in what you do, and care for those around you. Mom, Dad - I love you.

Of course many others played their part in this process. My Grandparents - Ginghy and Grandad - for always checking in with me (and helping make sure I was never falling behind) and my sisters for letting me take over the entire kitchen table to do work. I would like to specifically Thank John DeForest, Alexander Zhelyazkov, and Emily Lukas for reading early drafts of my Introduction. 

Final thanks to all the friends and mentors who were with me along the way
\cleardoublepage%
